---
title: "w241 project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data <- read.csv("w241_socialnorms/data/clean_data.csv")
data
```

```{r}
colnames(data)
```

```{r}
data[data$treatment == 0 & data$recall == 1,]

```


```{r}
data$gender
```


## Data Exploration

Distributions
```{r}
hist(data$outcome)
hist(data$page_1)
hist(data$page_2)
```

treatment group
```{r}
t_group <- data[data$treatment == 1,]
hist(t_group$outcome)
hist(t_group$page_1)
hist(t_group$page_2)
```

control group
```{r}
c_group <- data[data$treatment == 0,]
hist(c_group$outcome)
hist(c_group$page_1)
hist(c_group$page_2)
```



Regressions to test out:
- outcome ~
  - treatment
  - treatment + gender
  - treatment + 1st/2nd/transfer
  - treatment + race
  - treatment + recall
  - treatment + gender + 1st/2nd/transfer
  - treatment + gender + 1st/2nd/transfer + race
  - treatment + gender + 1st/2nd/transfer + race + political affiliation
  - treatment + gender + 1st/2nd/transfer + race + political affiliation + recall


- stop_svsh ~
  - treatment
  - treatment + gender
  - treatment + gender + 1st/2nd



- sexist_comment ~
  - treatment
  - treatment + gender
  

(not as significant but can use it to compare thoughts vs actions)
- receive_info ~

## Main Outcome as Outcome Variable

```{r}
outcome_lm0 <- lm(outcome ~ treatment, data = data)
summary(outcome_lm0)
```

```{r}
data$page_times <- data$page_1 + data$page_2

outcome_lm00 <- lm(outcome ~ treatment + page_times, data = data)
summary(outcome_lm00)
```




```{r}
outcome_lm1 <- lm(outcome ~ treatment + gender, data = data)
summary(outcome_lm1)
```

```{r}
outcome_lm11 <- lm(outcome ~ treatment * gender, data = data)
summary(outcome_lm11)
```



```{r}
data$first_second_year <- data$X1st_year + data$X2nd_year

outcome_lm2 <- lm(outcome ~ treatment + first_second_year * transfer, data = data)
summary(outcome_lm2)
```

```{r}
outcome_lm3 <- lm(outcome ~ treatment + asian + black + latino + native.hawaiian.or.pacific.islander + white + other. , data = data)
summary(outcome_lm3)
```

```{r}
# can't do this because it's a bad control
#outcome_lm4 <- lm(outcome ~ treatment * recall , data = data)
#summary(outcome_lm4)
```

```{r}
outcome_lm5 <- lm(outcome ~ treatment + gender + first_second_year * transfer  , data = data)
summary(outcome_lm5)
```

```{r}
outcome_lm6 <- lm(outcome ~ treatment + gender + first_second_year * transfer + asian + black + latino + native.hawaiian.or.pacific.islander + white + other., data = data)
summary(outcome_lm6)
```


```{r}
outcome_lm7 <- lm(outcome ~ treatment * gender + page_times + first_second_year * transfer , data = data)
summary(outcome_lm7)
```





## Stargazer

```{r}
cov0 <- vcovHC(outcome_lm0, type = "HC1")
robust_se0 <- sqrt(diag(cov0))

cov1 <- vcovHC(outcome_lm1, type = "HC1")
robust_se1 <- sqrt(diag(cov1))

cov2 <- vcovHC(outcome_lm2, type = "HC1")
robust_se2 <- sqrt(diag(cov2))

cov5 <- vcovHC(outcome_lm5, type = "HC1")
robust_se5 <- sqrt(diag(cov5))

# Produce initial stargazer table
# Copy results to regression-tables.tex, 
# Change covariate names, etc, then produce 
# regression-tables.pdf which will knit into
# draft report
stargazer(outcome_lm0,
          outcome_lm1,
          outcome_lm2,
          outcome_lm5, se = list(robust_se0, robust_se1, robust_se2, robust_se5),
          notes.append = TRUE, notes.align = "l",
          notes = "This will be replaced")

sandwich::vcovHC
```








```{r}
# who in treatment recalled the graphic?
nrow(data[data$treatment == 1 & data$recall == 1, ])

nrow(data[data$treatment == 1 & data$recall == 0, ])
```


## t test + power analysis
```{r}
ttest <- t.test(outcome ~ treatment, data = data)
d <- 2 * ttest$statistic /sqrt(nrow(data)-2)

cohend <- d^2 / 4
```


```{r}
# Power Test Method 2 (via power t-test) # use in paper
library(pwr)

data <- data.table(data)
treatment_group_ate <- data[, .(mean_outcome = mean(outcome)), keyby = treatment][,diff(mean_outcome)]
treatment_group_ate
treated <- data[treatment == 1, .N]
control <- data[treatment == 0, .N]

pwr.t2n.test(n1 = control, n2= treated, d = cohend, sig.level = 0.05, power = NULL)
```




```{r}
treatment <- data[data$treatment == 1,]
control <- data[data$treatment == 0,]


t.test(treatment$recall, control$recall)
```







## Playing Around


```{r}
data$read_weekly

#data$read_daily_more
```




```{r}
# cis men 1, other 0
lm0 <- lm(outcome ~ treatment * recall, data = data)
summary(lm0)

data$outcome
```


```{r}
lm1 <- lm(outcome ~ treatment + gender, data = data)
summary(lm1)
```


```{r}
# difference in the two groups based on treatment?
t.test(outcome ~ treatment, data = data)

2t/sqrt(n-2)

lm2 <- lm(outcome ~ treatment, data = data)
summary(lm2)

```

```{r}
lm3 <- lm(outcome ~ treatment + year , data = data)
summary(lm3)



lm4 <- lm(outcome ~ treatment + X1st_year + X2nd_year , data = data)
summary(lm4)
```

year???

```{r}
#data$X1st_year
#data$X2nd_year

data$first_half_college <- data$X1st_year + data$X2nd_year

lm4 <- lm(outcome ~ treatment + first_half_college , data = data)
summary(lm4)

```


```{r}
glm1 <- glm(outcome ~ gender + treatment, family=poisson, data = data)

summary(glm1)

```


```{r}
hist(data$outcome)
```

```{r}

```












